---
title: "Cyclistics Analysis in R"
author: "By: Abraham Cedeño"
phone: "+507 69827535"
date: "2022-11-11"
output: html_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
  
## Section 1: Data preparation (Import, transform, sort and filter)
***

### Import libraries
```{r, results='hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(ggpubr)
```

### Define paths to data sets
If you don't keep your data in the same directory as the code, adapt the path names.
```{r cars}
dir1 <- "~"
dir2 <- "Desktop"
dir3 <- "AC"
dir4 <- "Useful"
dir5 <- "Carrer"
dir6 <- "Cursos"
dir7 <- "2. Data analysis-Google"
dir8 <- "Capstone Case study 1"
dir9 <- "How I solved it"
dir10 <- "Data - cleaning - sorting - filtering" 
file_name  <- "Version 3"
PSDS_PATH <- file.path(dir1, dir2, dir3, dir4, dir5, dir6, dir7, dir8,dir9,dir10, file_name)
```

### Import csv files as data frames
```{r, results='hide', message=FALSE, warning=FALSE}
BikeTrips_2021_11_04_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2021_11_04_v31.csv'))
BikeTrips_2021_11_04_v32 <-  read_csv(file.path(PSDS_PATH, 'BikeTrips_2021_11_04_v32.csv'))
BikeTrips_2021_12_08_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2021_12_08_v3.csv'))
BikeTrips_2022_01_06_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_01_06_v3.csv'))
BikeTrips_2022_02_02_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_02_02_v3.csv'))
BikeTrips_2022_03_02_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_03_02_v3.csv'))
BikeTrips_2022_04_06_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_04_06_v3.csv'))
BikeTrips_2022_05_03_v3 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_05_03_v3.csv'))
BikeTrips_2022_06_03_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_06_03_v31.csv'))
BikeTrips_2022_06_03_v32 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_06_03_v32.csv'))
BikeTrips_2022_07_15_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_07_15_v31.csv'))
BikeTrips_2022_07_15_v32 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_07_15_v32.csv'))
BikeTrips_2022_08_05_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_08_05_v31.csv'))
BikeTrips_2022_08_05_v32 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_08_05_v32.csv'))
BikeTrips_2022_09_08_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_09_08_v31.csv'))
BikeTrips_2022_09_08_v32 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_09_08_v32.csv'))
BikeTrips_2022_10_11_v31 <- read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_10_11_v31.csv'))
BikeTrips_2022_10_11_v32 <-read_csv(file.path(PSDS_PATH, 'BikeTrips_2022_10_11_v32.csv'))
```

### Change column names
To ensure that I could merge the data frames together later, I checked the column names and corrected any spelling mistakes as needed to make them consistent across all the data frames.
```{r, results='hide', message=FALSE, warning=FALSE}
colnames(BikeTrips_2021_12_08_v3)[4] <- "started_time"
colnames(BikeTrips_2022_02_02_v3)[4] <- "started_time"
colnames(BikeTrips_2022_02_02_v3)[5] <- "end_date"
colnames(BikeTrips_2022_02_02_v3)[6] <- "end_time"
```

### Merge all data frames into 1
```{r, results='hide', message=FALSE, warning=FALSE}
BikeTrips_todos <- rbind(BikeTrips_2021_11_04_v31, BikeTrips_2021_11_04_v32, BikeTrips_2021_12_08_v3, BikeTrips_2022_01_06_v3, BikeTrips_2022_02_02_v3, BikeTrips_2022_03_02_v3, BikeTrips_2022_04_06_v3, BikeTrips_2022_05_03_v3, BikeTrips_2022_06_03_v31, BikeTrips_2022_06_03_v32, BikeTrips_2022_07_15_v31, BikeTrips_2022_07_15_v32, BikeTrips_2022_08_05_v31, BikeTrips_2022_08_05_v32, BikeTrips_2022_09_08_v31, BikeTrips_2022_09_08_v32, BikeTrips_2022_10_11_v31, BikeTrips_2022_10_11_v32)
```

### Transform dataype from chr to date
```{r}
class(BikeTrips_todos$started_date)
BikeTrips_todos$started_date <- mdy(BikeTrips_todos$started_date)
class(BikeTrips_todos$started_date)
class(BikeTrips_todos$end_date)
BikeTrips_todos$end_date <- mdy(BikeTrips_todos$end_date)
class(BikeTrips_todos$end_date)
```
### Sort ascending according to started_date and started_time
```{r, results='hide', message=FALSE, warning=FALSE}
BikeTrips_todos<- arrange(BikeTrips_todos,started_date,started_time)
```

  
## Section 2: Data process (clean)
***

### Duplicates
I've used the function duplicated and saves the duplicates in a dataframe called duplicates (The I'ds where duplicated but the data was different)

```{r}
duplicates <-BikeTrips_todos[duplicated(BikeTrips_todos$ride_id)|duplicated(BikeTrips_todos$ride_id, fromLast=TRUE),]
```
Therefore, I concluded that there were no duplicates.

### Blanks or mispellings in CHR columns
I've check max and min length of CHR datatypes to find if there were any blanks (below some of them)
```{r}
max(nchar(BikeTrips_todos$rideable_type))
min(nchar(BikeTrips_todos$rideable_type))
```
The only 3 options are "classic_bike", "electric_bike" and "docked_bike" which have 12, 13 and 11 characters respectively, therefore, I concluded that there were no blanks.

### Ranges of NUM columns 
I've check max and min values of NUM datatypes to find if there were any blanks (below some of them)
```{r}
max(BikeTrips_todos$start_lng)
min(BikeTrips_todos$start_lng)
```

Longitudes could range from -180 to 0 (West) or 0 to 180 (east). Therefore, the longitudes are inside the range. Altough, Chicago longides are between -87.63 to -87.52 degrees West, which means that there are some values out of that range, we will have to decide what to do with those measure later on.

### Count values with the length expected
I've used this function which is similar to countIF to know how many observations had more than 8 characters
```{r}
sum(nchar(BikeTrips_todos$rideable_type) > 8, na.rm=TRUE)
```
All observations must fall within this range, as the "BikeTrips_todos" data frame has 5528236 observations, we conclude that the "count" is correct.

### Count values with the latitude expected
I've used with this function which is similar to countIF to know how many observations had latitudes above 8º.
```{r}
sum(BikeTrips_todos$start_lat > 8, na.rm=TRUE)
```
All observations must fall within this range, as the Chicago's latitude range is between 41.6ºN and 42ºN, the data frame has 5528236 observations, we conclude that the "count" is correct.

### Erase all blanks if there are
I've use this function to erase all blank spaces before and after all characters 
```{r}
BikeTrips_todos <- BikeTrips_todos %>% mutate(across(where(is.character), str_trim))
```

  
  
## Section 3: Analysis phase (calculations, visualizations, explore data)

### 1. What was the percentage distribution of bike preferences?
***

#### Calculus of % distribution
I've created a function called conteo. This function does the following:

1. Filters the "BikeTrips_todos" data frame by casual or member.

2. Count the rides per type of ride (classic, electric, docked).

3. Creates a new column with the % calculations.

4. Scale the percentages in a new column called "lables" as characters to plot later on.

```{r}
conteo<- function(casual_or_member) {BikeTrips_todos %>%
  filter(member_casual == casual_or_member) %>%
  group_by(rideable_type) %>% # Variable to be transformed
  count(rideable_type)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))  }
```

#### Apply function and visualize tables
```{r}
conteoA <- conteo("casual")
conteoB <- conteo("member")
conteoA
conteoB
```


#### Pie chart visualizations

```{r, echo=FALSE, message=FALSE, warning=FALSE }
# I've created a plot to visualise bike preference for casual riders in a pie chart
a1 <- ggplot(conteoA, aes(x ="", y = perc, fill = rideable_type)) +
  geom_col(color="white") +
  scale_fill_manual(values=c("#cce6ea", "#d9f150", "#3aaca6"))+
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=5) +
  coord_polar(theta = "y") +
  labs(title = "         Bike preference - casual riders", y= "%", x= "%")
a1

# I've created a plot to visualise bike preference for member riders in a pie chart
b1 <- ggplot(conteoB, aes(x ="", y = perc, fill = rideable_type)) +
  geom_col(color="white") +
  scale_fill_manual(values=c("#cce6ea", "#3aaca6"))+
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=5) +
  coord_polar(theta = "y") +
  labs(title = "         Bike preference - member riders", y= "%", x= "%")
b1

# Finally, I plot the two charts one above the other using the ggarrange function
theme_set(theme_grey())
vis_question1 <- ggarrange(a1, b1,
                    ncol = 2, nrow = 1)
vis_question1

```


### 2. How is the service usage distributed over the week?
***

#### Order days of the week
Default is for Sunday to be the first day on R, I used the function factor to order the "day_of_week" column
```{r, results='hide', message=FALSE, warning=FALSE}
BikeTrips_todos_ordenado_por_dia<-BikeTrips_todos
BikeTrips_todos_ordenado_por_dia$day_of_week <- factor(BikeTrips_todos_ordenado_por_dia$day_of_week, c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
```

#### Counts the number of trips per day of the week
I've created a function called day. This function does the following:

1. Filters the "BikeTrips_todos_ordenado_por_dia" data frame by casual or member.

2. Sort and count the rides per day of the week (monday, tuesday, etc).

3. Creates a new column with the % calculations.

4. Scale the percentages in a new column called "labels" as characters to plot later on.

```{r}
day <- function(casual_or_member) {BikeTrips_todos_ordenado_por_dia %>%
  filter(member_casual == casual_or_member) %>%
  group_by(day_of_week) %>% # Variable to be transformed
  count(day_of_week)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc)) } 
```

#### Apply function and visualize tables
```{r}
day_casual <- day("casual")
day_member <- day("member")
day_casual
day_member
```

#### Bar and pie chart visualizations
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I've created a plot to visualize day preference for casual riders in a pie chart
a2 <- ggplot(day_casual, aes(x ="", y = perc, fill = day_of_week)) +
  geom_col(color="white") +
  scale_fill_manual(values=c("#cce6ea", "#d9f150", "#3aaca6", "#AB613A", "#F7B03B", "#F7746D","#32AB60"))+
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "         Day preference - casual riders", y= "%", x= "%")
a2

# I've created a plot to visualize day preference for member riders in a pie chart
b2 <- ggplot(day_member, aes(x ="", y = perc, fill = day_of_week)) +
  geom_col(color="white") +
  scale_fill_manual(values=c("#cce6ea", "#d9f150", "#3aaca6", "#AB613A", "#F7B03B", "#F7746D","#32AB60"))+
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "         Day preference - member riders", y= "%", x= "%")
b2

# I plotted the two graphs in one image
# vis_question2 <- ggarrange(a2, b2,
                          # ncol = 1, nrow = 2)
# vis_question2


# I created a plot to visualize day preference per type of rider as bar chart
c2 <- ggplot(BikeTrips_todos_ordenado_por_dia, aes(x = day_of_week, fill = member_casual)) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  scale_fill_manual(values=c("#3aaca6", "#d9f150"))+
  labs(title = "         Day pereference per type of rider", y= "count of trips", x= "day of the week")

# Turn of exponentials in the plotting
options(scipen=999)

c2
```

## 3. How is the service usage distributed over a day?
***

#### Counts the number of trips per time second by second
I've created a function called "calculate_bike_trip_counts". This function does the following:

1. The if statement checks if member_type is provided. If it is, the function filters data to only include rows where the member_casual column matches member_type. If it isn't provided, all rows are included.

2. The function then groups the rows of the data data frame by started_time column and counts the number of occurrences of each unique value in the started_time column, sorted in descending order. The result is a new data frame trip_counts that shows the count of bike trips for each unique started_time value.

3. Finally, the function returns the trip_counts data frame.

```{r}
calculate_bike_trip_counts <- function(data, member_type = NULL) {
  if (!is.null(member_type)) {
    data <- data %>% filter(member_casual == member_type)
  }
  trip_counts <- data %>%
    group_by(started_time) %>%
    count(started_time, sort = TRUE)
  return(trip_counts)
}
```

#### Apply function
```{r}
Tiempo_conteo <- calculate_bike_trip_counts(BikeTrips_todos, NULL)
Tiempo_conteo_casual <- calculate_bike_trip_counts(BikeTrips_todos, "casual")
Tiempo_conteo_member <- calculate_bike_trip_counts(BikeTrips_todos, "member")
```

#### Convert time to POSIXct for plotting
I've created a function called "convert_and_adjust_time". This function does the following:

1. Takes a data frame and converts the started_time column to POSIXct format 

2. Adjusts any values less than the Unix epoch time to be one day ahead.
```{r}
convert_and_adjust_time <- function(df) {
  df %>%
    mutate(started_time = as.POSIXct(started_time),
           started_time = if_else(started_time < as.POSIXct('1970-01-01 00:00:00', 'UTC'), started_time + 86400, started_time))
}
```

#### Apply function
```{r}
Tiempo_conteo2 <- convert_and_adjust_time(Tiempo_conteo)
Tiempo_conteo_casual2 <- convert_and_adjust_time(Tiempo_conteo_casual)
Tiempo_conteo_member2 <- convert_and_adjust_time(Tiempo_conteo_member)
```

#### Dot plot visualization
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I assigned the plot of casual riders into a3
a3 <- ggplot(data = Tiempo_conteo_casual2, mapping = aes(x = started_time, y = n)) +  geom_point(size=3, alpha=0.5, color="#f5746c") + geom_smooth()+
  labs(title="# of trips per time of the day for casual riders- last 12 months", y= "count of trips", x= "time measured by seconds")+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="none")+
  scale_x_datetime(date_labels = '%H:%M', 
                   limits = c(as.POSIXct('1970-01-01 00:00:00', tz = 'UTC'), 
                              as.POSIXct('1970-01-02 00:00:00', tz = 'UTC')), 
                   breaks = '2 hour')

a3


# I assigned the plot of member riders into b3
b3 <- ggplot(data = Tiempo_conteo_member2, mapping = aes(x = started_time, y = n)) +  geom_point(size=3, alpha=0.5, color="#19b5bb") + geom_smooth()+
  labs(title="# of trips per time of the day for member riders- last 12 months", y= "count of trips", x= "time measured by seconds") +
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="none")+
  scale_x_datetime(date_labels = '%H:%M', 
                   limits = c(as.POSIXct('1970-01-01 00:00:00', tz = 'UTC'), 
                              as.POSIXct('1970-01-02 00:00:00', tz = 'UTC')), 
                   breaks = '2 hour')
  b3


# I created a picture with both visualizations a3 and b3
vis_question3 <- ggarrange(a3, b3,
                           ncol = 1, nrow = 2)
vis_question3
```

## 4. What is the average trip duration?
***
#### Convert time to POSIXct for plotting
I've created a function called "calculate_ride_length". This function does the following:

1. Takes in a data frame data and an optional argument member_type. The if statement checks if member_type is provided. If it is, the function filters data to only include rows where the member_casual column matches member_type. If it isn't provided, all rows are included.

2. The function then modifies the ride_length column of the data data frame by converting it to POSIXct format and adding 86400 seconds (one day) if the ride_length is less than 1970-01-01 00:00:00 in UTC time. This is done using the mutate and if_else functions from dplyr.

3. Finally, the function returns the modified data data frame.

```{r}
calculate_ride_length <- function(data, member_type = NULL) {
  if (!is.null(member_type)) {
    data <- data %>% filter(member_casual == member_type)
  }
  data <- data %>% mutate(
    ride_length = as.POSIXct(ride_length),
    ride_length = if_else(ride_length < as.POSIXct('1970-01-01 00:00:00', 'UTC'), ride_length + 86400, ride_length)
  )
  return(data)
}
```

```{r}
BikeTrips_todos_casual <- calculate_ride_length(BikeTrips_todos, "casual")

BikeTrips_todos_member <- calculate_ride_length(BikeTrips_todos, "member")
```



#### Calculate mean and median for casual and member riders
```{r}
# I calculated the mean for casual riders and convert it into a numeric value
mean1 <- BikeTrips_todos_casual %>%
   summarize(mean(ride_length))

mean1_numeric <- as.numeric(mean1)
mean1


# I calculated the median for casual riders and convert it into a numeric value
median_casual <- BikeTrips_todos_casual %>%
  summarize(median(ride_length))

median1_numeric <- as.numeric(median_casual)
median_casual


# I calculated the mean for member riders and convert it into a numeric value
mean2 <- BikeTrips_todos_member %>%
  summarize(mean(ride_length))

mean2_numeric <- as.numeric(mean2)
mean2

# I calculated the median for casual riders and convert it into a numeric value
median_member <- BikeTrips_todos_member %>%
  summarize(median(ride_length))

median2_numeric <- as.numeric(median_member)
median_member
```

#### Create 2 vertical lines with the mean for plotting
```{r}
mean1_vertical <- data.frame(x=c(mean1_numeric,mean1_numeric), y=c(-5,5))

mean2_vertical <- data.frame(x=c(mean2_numeric,mean2_numeric), y=c(-5,5))
```

#### Histogram visualizations
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# I plotted a histogram with the mean 
ggplot(BikeTrips_todos_casual, aes(x=ride_length)) + geom_histogram(fill="#3aaca6", color="white") +
  geom_vline(data=mean1_vertical, aes(x, y), xintercept = mean1_numeric , color="#AB613A")+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_datetime(date_labels = '%H:%M', 
                   limits = c(as.POSIXct('1970-01-01 00:00:00', tz = 'UTC'), 
                              as.POSIXct('1970-01-01 01:00:00', tz = 'UTC')), 
                   breaks = '10 mins') +
  labs(title = "Distribution of trip duration and average trip duration - Casual riders", y= "count of trips", x= "trip duration")




# I plotted a histogram with the mean 
ggplot(BikeTrips_todos_member, aes(x=ride_length)) + geom_histogram(fill="#3aaca6", color="white") +
  geom_vline(data=mean2_vertical, aes(x, y), xintercept = mean2_numeric , color="#AB613A")+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_datetime(date_labels = '%H:%M', 
                   limits = c(as.POSIXct('1970-01-01 00:00:00', tz = 'UTC'), 
                              as.POSIXct('1970-01-01 01:00:00', tz = 'UTC')), 
                   breaks = '10 mins') +
  labs(title = "Distribution of trip duration and average trip duration - Member riders", y= "count of trips", x= "trip duration")

```


### 5. What is the preferred station for starting trips?
***

#### Top ten start stations for member and casual riders

```{r}
# I printed the top ten start stations for member riders
start_station_member <- BikeTrips_todos %>%
  filter(member_casual == "member") %>%
  count(start_station_name, sort = TRUE)

start_station_member %>%
print(n=11 )


# I printed the top ten start stations for casual riders
start_station_casual <- BikeTrips_todos %>%
  filter(member_casual == "casual") %>%
  count(start_station_name, sort = TRUE) 

  start_station_casual %>%
  print(n=11 )
  
```


#### Top ten end stations for member and casual riders
```{r}
 # I printed the top ten end stations for casual riders

end_station_casual <- BikeTrips_todos %>%
  filter(member_casual == "casual") %>%
  count(end_station_name, sort = TRUE) 

end_station_casual %>%
print(n = 11)


# I printed the top ten end stations for member riders
end_station_member <- BikeTrips_todos %>%
  filter(member_casual == "member") %>%
  count(end_station_name, sort = TRUE) 


end_station_member %>%
  print(n = 11)
```

### 6. How are the trip start points distributed geographically?
***

#### Range of starting latitude of trips
```{r}
max(BikeTrips_todos$start_lat)
min(BikeTrips_todos$start_lat)
```

#### Histogram visualization of starting latitude of trips
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(BikeTrips_todos, aes(x=start_lat)) + geom_histogram(fill="#3aaca6", color="white") +
  facet_wrap(~member_casual)+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_continuous(limits = c(41.75, 42.1)) +
  labs(title = "Distribution of starting latitude of trips for casual and member riders", y= "count of trips", x= "starting latitude")

```

#### Range of starting longitude of trips
```{r}
max(BikeTrips_todos$start_lng)
min(BikeTrips_todos$start_lng)
```

#### Histogram visualization of starting longitude of trips
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(BikeTrips_todos, aes(x=start_lng)) + geom_histogram(fill="#3aaca6", color="white") +
  facet_wrap(~member_casual)+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_continuous(limits = c(-87.8, -87.55)) +
  labs(title = "Distribution of starting longitude of trips for casual and member riders", y= "count of trips", x= "starting longitude")
```

#### Range of ending latitude of trips
```{r}
max(BikeTrips_todos$end_lat)
min(BikeTrips_todos$end_lat)
```

#### Histogram visualization of ending latitude of trips
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(BikeTrips_todos, aes(x=end_lat)) + geom_histogram(fill="#3aaca6", color="white") +
  facet_wrap(~member_casual)+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_continuous(limits = c(41.70, 42.10)) +
  labs(title = "Distribution of ending latitudes of trips for casual and member riders", y= "count of trips", x= "ending latitude")
```





#### Range of ending longitude of trips
```{r}
max(BikeTrips_todos$end_lng)
min(BikeTrips_todos$end_lng)
```

#### Histogram visualization of ending longitude of trips
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(BikeTrips_todos, aes(x=end_lng)) + geom_histogram(fill="#3aaca6", color="white") +
  facet_wrap(~member_casual)+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  scale_x_continuous(limits = c(-87.80, -87.55)) +
  labs(title = "Distribution of ending longitudes of trips for casual and member riders", y= "count of trips", x= "ending longitude")
```