---
title: "Marketing Analytics"
author: "Abraham Cedeño"
date: "2023-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section 1: Data preparation (Import, transform, sort and filter)
***

### Import libraries
```{r message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(stringr)
library(ggpubr)
library(knitr)

```

### Define paths to data sets
If you don't keep your data in the same directory as the code, adapt the path names.
```{r}
dir1 <- "~"
dir2 <- "Desktop"
dir3 <- "AC"
dir4 <- "Useful"
dir5 <- "Carrer"
dir6 <- "Skills "
dir7 <- "3. Skills para trabajo"
dir8 <- "10. R data science, statistics, machine learning"
dir9 <- "Portfolio analysis" 
dir10 <- "3. Marketing Analytics" 
file_name  <- "Data"
PSDS_PATH <- file.path(dir1, dir2, dir3, dir4, dir5, dir6, dir7, dir8, dir9, dir10, file_name)
```

### Import csv files as data frames
```{r, results='hide', message=FALSE, warning=FALSE}
Data <- read_csv(file.path(PSDS_PATH, 'ml_project1_data.csv'))
```

### Sort ascending according to ID
```{r, results='hide', message=FALSE, warning=FALSE}
Data<- arrange(Data,ID)
```

### Transform Year_Birth to Age
It would be useful to have a feature with the age of the clients. 

As the last date in the data is on june of 2014, we are going to assume that we are performing this analysis in 2014 for the age calculations.

```{r}
Data <- Data %>%
  mutate(Age = 2014 - Year_Birth)
```

## Section 2: Data process (clean)
***

### Explore the data frame

```{r}
str(Data)
```

#### Categorial feature options

```{r}
#Unique categories in each categorical column
unique(Data$Education)
unique(Data$Marital_Status)
```
As it can observed, there are no trailing or leading spaces, misspelings, or blank spaces, therefore, this portion of the data is cleaned.

#### About the data
```{r, echo=FALSE, message=FALSE, warning=FALSE}
summary_features <- data.frame(
  Group = c("ID", "Age", "Income", "Kidhome", "Teenhome", "Dt_Customer", "Recency", "MntWines","MntFruits","MntMeatProducts","MntFishProducts","MntSweetProducts","MntGoldProds","NumDealsPurchases","NumWebPurchases","NumCatalogPurchases","NumStorePurchases","NumWebVisitsMonth","AcceptedCpm1", "AcceptedCpm2", "AcceptedCpm3", "AcceptedCpm4", "AcceptedCpm5", "Complain", "Z_CostContact", "Z_Revenue", "Response","Education", "Marital Status"),
    
  Range = c(paste(range(Data$ID), collapse = "-"),
            paste(range(Data$Age), collapse = "-"),
            paste(range(Data$Income,na.rm = TRUE), collapse = "-"),
            paste(range(Data$Kidhome), collapse = "-"),
            paste(range(Data$Teenhome), collapse = "-"),
            paste(range(Data$Dt_Customer), collapse = " to "),   
            paste(range(Data$Recency), collapse = "-"),
            paste(range(Data$MntWines), collapse = "-"),
            paste(range(Data$MntFruits), collapse = "-"),

            paste(range(Data$MntMeatProducts), collapse = "-"),
            paste(range(Data$MntFishProducts), collapse = "-"),
            paste(range(Data$MntSweetProducts), collapse = "-"),
            paste(range(Data$MntGoldProds), collapse = "-"),
            paste(range(Data$NumDealsPurchases), collapse = "-"),
            paste(range(Data$NumWebPurchases), collapse = "-"),
            paste(range(Data$NumCatalogPurchases), collapse = "-"),

            paste(range(Data$NumStorePurchases), collapse = "-"),
            paste(range(Data$NumWebVisitsMonth), collapse = "-"),
            paste(range(Data$AcceptedCmp1), collapse = "-"),
            paste(range(Data$AcceptedCmp2), collapse = "-"),
            paste(range(Data$AcceptedCmp3), collapse = "-"),
            paste(range(Data$AcceptedCmp4), collapse = "-"),
            paste(range(Data$AcceptedCmp5), collapse = "-"),

            paste(range(Data$Complain), collapse = "-"),
            paste(range(Data$Z_CostContact), collapse = "-"),
            paste(range(Data$Z_Revenue), collapse = "-"),
            paste(range(Data$Response), collapse = "-"), "-", "-"),
  
     Data_Type = c("Categorical nominal","Numeric discrete","Numeric continuous", "Numeric discrete", "Numeric discrete","Numeric discrete", "Numeric discrete","Numeric continuous","Numeric continuous","Numeric continuous","Numeric continuous","Numeric continuous","Numeric continuous","Numeric discrete","Numeric discrete","Numeric discrete","Numeric discrete","Numeric discrete","Categorical nominal","Categorical nominal","Categorical nominal","Categorical nominal","Categorical nominal","Categorical nominal", "Not sure", "Not sure","Categorical nominal","Categorical nominal","Categorical nominal")

)
```

```{r , echo=FALSE, message=FALSE, warning=FALSE}
kable(summary_features, caption = "Exploring the features characteristics")
```
It can be observed that the ranges of numerical data are as expected, therefore, this portion of the data is cleaned.

### Duplicates
```{r}
duplicates <- duplicated(Data$ID)
num_true <- sum(duplicates)
print(num_true)
remove(duplicates,num_true)
```
We can conclude that there are no duplicates.

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
Unique_Data<- unique (Data[ , c("ID", "Year_Birth", "Income", "Kidhome", "Teenhome", "Dt_Customer", "Recency", "MntWines","MntFruits","MntMeatProducts","MntFishProducts","MntSweetProducts","MntGoldProds","NumDealsPurchases","NumWebPurchases","NumCatalogPurchases","NumStorePurchases","NumWebVisitsMonth","AcceptedCmp1", "AcceptedCmp2", "AcceptedCmp3", "AcceptedCmp4", "AcceptedCmp5", "Complain", "Z_CostContact", "Z_Revenue", "Response", "Education", "Marital_Status") ] )
remove(Unique_Data)
```


## Section 3: Exploratory Data Analysis
***
Before we start, it would be useful to know how many Responses we had in our test.

We know that there are 2240 observations and that Response is a binary datatype (0 or 1). 
```{r}
table(Data$Response)
```

### Categorical features exploration
I'll start by exploring the categorical features (Education and Marital_Status).

***

#### Education
```{r, results='hide',echo=FALSE, message=FALSE, warning=FALSE}
#ggplot(Data, aes(x = Education, fill = factor(Response))) +
 # geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  #labs(title = "Education level per Response", y= "Count per Response", x= "Categories")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Education <- function(True_False) {Data %>%
  filter(Response == True_False) %>%
  group_by(Education) %>% # Variable to be transformed
  count(Education)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc)) } 
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Education0 <- Education(0)
Education1 <- Education(1)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I've created a plot to visualize day preference for casual riders in a pie chart
ggplot(Education0, aes(x ="", y = perc, fill = Education)) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Education level for 0 response", y= "%", x= "%")

ggplot(Education1, aes(x ="", y = perc, fill = Education)) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Education level for 1 response", y= "%", x= "%")
```


##### Observations for level of education
We noticed that there is a pattern worth studying forward: 

*People with PhD's tend to respond better to the ad.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
#### Marital Status
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#ggplot(Data, aes(x = Marital_Status, fill = factor(Response))) +
 # geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  #labs(title = "Marital_Status per Response", y= "Count per Response", x= "Categories")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Marital_Status <- function(True_False) {Data %>%
  filter(Response == True_False) %>%
  group_by(Marital_Status) %>% # Variable to be transformed
  count(Marital_Status)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc)) } 
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Marital_Status0 <- Marital_Status(0)
# Extract the first 5 characters
Marital_Status0$labels <- paste0(substr(Marital_Status0$labels, start = 1, stop = 4), substr(Marital_Status0$labels, start = 7, stop = 7))  
# Replace the 6th character with the 7th character

Marital_Status1 <- Marital_Status(1)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I've created a plot to visualize day preference for casual riders in a pie chart
ggplot(Marital_Status0, aes(x ="", y = perc, fill = Marital_Status)) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Marital Status for 0 response", y= "%", x= "%")

ggplot(Marital_Status1, aes(x ="", y = perc, fill = Marital_Status)) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Marital Status for 1 response", y= "%", x= "%")
```


##### Observations for Marital Status
We noticed that there is a pattern worth studying forward: 

*When customers are not in a relationship ("Single", "Widow", "Divorced") their response to the ad increases. 

*The opposite effect is true also, when customers are in a relationship ("Married" or "Toghether") their respond to the ad decreases.

In the next section (Statistical analysis), we will determine wether these differences are **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
#### Complain
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x = Complain, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "Response of people who complain vs people who didn't", y= "Count per Response", x= "Accepted or nor Campaign 1")
```


##### Observations for Complain
We noticed that there is a pattern worth studying forward: 

*People who complain are way more likely to not respond to campaign 6.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.


***
#### Response to previous camapaigns vs Response to target campaign
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x = AcceptedCmp1, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "People behavior to Campaign 1 vs Response", y= "Count per Response", x= "Accepted or nor Campaign 1")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x = AcceptedCmp2, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "People behavior to Campaign 2 vs Response", y= "Count per Response", x= "Accepted or nor Campaign 2")

ggplot(Data, aes(x = AcceptedCmp3, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "People behavior to Campaign 3 vs Response", y= "Count per Response", x= "Accepted or nor Campaign 3")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x = AcceptedCmp4, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "People behavior to Campaign 4 vs Response", y= "Count per Response", x= "Accepted or nor Campaign 4")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x = AcceptedCmp5, fill = factor(Response))) +
  geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
  labs(title = "People behavior to Campaign 5 vs Response", y= "Count per Response", x= "Accepted or nor Campaign 5")
```



##### Observations for response to previous campaigsn
We noticed that there is a pattern worth studying forward: 

*People that responded positively to our previous campaigns are more likely to respond positively to campaign 6.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.


### Numerical discrete features exploration
Now it's time to study the numerical discrete features (Kidhome, Teenhome, AcceptedCpm[1,2,3,4,5], Complain), these can be explored similarly to the categorical features.

***
##### Kids Home
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#ggplot(Data, aes(x = factor(Kidhome), fill = factor(Response))) +
 # geom_bar(position= "dodge", alpha =1, width = 0.75, color="white") +
 # labs(title = "Kidhome per Response", y= "Count per Response", x= "Categories")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Kidhome <- function(True_False) {Data %>%
  filter(Response == True_False) %>%
  group_by(Kidhome) %>% # Variable to be transformed
  count(Kidhome)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc)) } 
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Kidhome0 <- Kidhome(0)
Kidhome1 <- Kidhome(1)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I've created a plot to visualize day preference for casual riders in a pie chart
ggplot(Kidhome0, aes(x ="", y = perc, fill = factor(Kidhome))) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Kids home for 0 response", y= "%", x= "%")

ggplot(Kidhome1, aes(x ="", y = perc, fill = factor(Kidhome))) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Kids home for 1 response", y= "%", x= "%")
```


##### Observations for Kids Home

We noticed that there is a pattern worth studying forward: 

*The more kids people have, the less likely they are to respond to our ads. 

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
##### Teens Home
```{r, echo=FALSE, message=FALSE, warning=FALSE}
TeensHome <- function(True_False) {Data %>%
  filter(Response == True_False) %>%
  group_by(Teenhome) %>% # Variable to be transformed
  count(Teenhome)  %>% 
  ungroup() %>% 
  mutate(perc = n / sum(n)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc)) } 
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
TeensHome0 <- TeensHome(0)
TeensHome1 <- TeensHome(1)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# I've created a plot to visualize day preference for casual riders in a pie chart
ggplot(TeensHome0, aes(x ="", y = perc, fill = factor(Teenhome))) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Teens home for 0 response", y= "%", x= "%")

ggplot(TeensHome1, aes(x ="", y = perc, fill = factor(Teenhome))) +
  geom_col(color="white") +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5), size=4) +
  coord_polar(theta = "y") +
  labs(title = "Teens home for 1 response", y= "%", x= "%")
```


##### Observations for Teens Home

We noticed that there is a pattern worth studying forward: 

*The more teens people have, the less likely they are to respond to our ads. 

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
#### Age

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=Age, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Age') + 
  theme_bw()
```



We notice that there are a few outliers above 100, probably these people found the cure to death, but just to be sure we decided to exclude them.

```{r}
Data <- Data %>%
  filter(Age < 100)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=Age, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Age') + 
  theme_bw()
```


##### Observations for Age
As it is observed in the boxplot, there's a minimal difference in age for the people who had a positive response to our ad vs those who didn't.

Therefore, we will **not pursue a statistical analysis** nor use this feature in the model to predict the response.


***
#### Recency

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=Recency, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Recency (days since last purchase)') + 
  theme_bw()
```


##### Observations for Recency
We noticed that there is a pattern worth studying forward: 

*People with lower recency tend to respond better to the ad.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.


***
#### NumDealsPurchases
```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumDealsPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumDealsPurchases') + 
  theme_bw()
```



We notice that there are a few outliers above 7.5, we decided to exclude them.

```{r}
Data <- Data %>%
  filter(NumDealsPurchases < 7.5)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumDealsPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumDealsPurchases') + 
  theme_bw()
```


##### Observations for NumDealsPurchases
As it is observed in the boxplot, there's a minimal difference in NumDealsPurchases for the people who had a positive response to our ad vs those who didn't.

Therefore, we will **not pursue a statistical analysis** nor use this feature in the model to predict the response.

***
#### NumWebPurchases
```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumWebPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumWebPurchases') + 
  theme_bw()
```


We notice that there are a few outliers above 15, we decided to exclude them.

```{r}
Data <- Data %>%
  filter(NumWebPurchases < 15)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumWebPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumWebPurchases') + 
  theme_bw()
```


##### Observations for NumWebPurchases
We noticed that there is a pattern worth studying forward: 

*People with higher NumWebPurchases tend to respond better to the ad.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
#### NumCatalogPurchases
```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumCatalogPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumCatalogPurchases') + 
  theme_bw()
```


We notice that there are a few outliers above 15, we decided to exclude them.

```{r}
Data <- Data %>%
  filter(NumCatalogPurchases < 15)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumCatalogPurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumCatalogPurchases') + 
  theme_bw()
```


##### Observations for NumCatalogPurchases
We noticed that there is a pattern worth studying forward: 

*People with higher NumCatalogPurchases tend to respond better to the ad.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.



***
#### NumStorePurchases
```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumStorePurchases, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumStorePurchases') + 
  theme_bw()
```


##### Observations for NumStorePurchases
As it is observed in the boxplot, there's a minimal difference in NumStorePurchases for the people who had a positive response to our ad vs those who didn't.

Therefore, we will **not pursue a statistical analysis** nor use this feature in the model to predict the response.

***
#### NumWebVisitsMonth

```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumWebVisitsMonth, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumWebVisitsMonth') + 
  theme_bw()
```


We notice that there are a few outliers above 12, we decided to exclude them.

```{r}
Data <- Data %>%
  filter(NumWebVisitsMonth < 12)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot(Data, aes(x=factor(Response), y=NumWebVisitsMonth, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='NumWebVisitsMonth') + 
  theme_bw()
```


##### Observations for NumWebVisitsMonth
We noticed that there is a pattern worth studying forward: 

*The distribution for people who response better to the ad is wider, therefore the observations that are closer to the tales can help our model predict better the outcome.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.

***
#### Dt_Customer	

```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Responses <- Data %>%
  group_by(Dt_Customer, Response) %>%
  count(Dt_Customer, sort = TRUE) %>%
  return(Dt_Customer)
```


```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Count_Responses, aes(x=Dt_Customer,fill=factor(Response))) + geom_histogram(bins=20, width = 0.75, color="white") +
  geom_vline(xintercept = 5, linetype = "dashed", alpha = 0.5)+
  facet_wrap(~Response)+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right")+
  labs(title = "Histogram for Date enrollment vs Response", y= "Number of responses", x= "Date of customer enrollment with the company")

```

##### Observations for Dt_Customer
We noticed that there is a pattern worth studying forward: 

*The farther the day of enrollment with the company, the better the clients respond to the ad.

In the next section (Statistical analysis), we will determine wether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.


### Numerical features exploration
Now it's time to study the numerical features

***
#### Income

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Load ggplot2 library
options(scipen=999)

ggplot(Data, aes(x=factor(Response), y=Income, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Income (in USD)') + 
  theme_bw()
```


We notice that there are a few outliers above 140000, we decided to exclude them:
```{r}
Data <- Data %>%
  filter(Income  < 140000)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=Income, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Income (in USD)') + 
  theme_bw()
```

```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=Income,fill=factor(Response))) + geom_histogram(bins=20, width = 0.75, color="white") +
  geom_vline(xintercept = 5, linetype = "dashed", alpha = 0.5)+
  facet_wrap(~factor(Response))+
  theme_bw()+
  theme(axis.text.x = element_text(hjust = 1,family="Times", face="bold", size=12, color="black"), 
        axis.title.x = element_text(family="Times", face="bold", size=16, color="black"),
        axis.text.y = element_text(family="Times", face="bold", size=12, color="black"),
        axis.title.y = element_text(family="Times", face="bold", size=16, color="black"),
        strip.text = element_text(size=10, face="bold"),
        plot.title = element_text(size=20, face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(family="Times", color = "black", size = 16,face="bold"),
        legend.position="right") +
  labs(y= "Number of clients", x= "Income (in usd)")

```


##### Observations for Income
We noticed that there is a pattern worth studying forward: 

*The higher the client's income, the better the clients respond to the ad.

In the next section (Statistical analysis), we will determine whether this difference is **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.



***
#### MntWines	
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntWines, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on Wines (in USD)') + 
  theme_bw()
```

***
#### MntFruits	
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntFruits, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on fruits (in USD)') + 
  theme_bw()
```

***
#### MntMeatProducts	
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntMeatProducts, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on meat (in USD)') + 
  theme_bw()
```

***
#### MntFishProducts	
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntFishProducts, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on fish (in USD)') + 
  theme_bw()
```


***
#### MntSweetProducts	
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntSweetProducts, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on Sweet products (in USD)') + 
  theme_bw()
```


***
#### MntGoldProds
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Data, aes(x=factor(Response), y=MntGoldProds, fill=factor(Response))) + 
  geom_boxplot() +
  labs(y='Money spent on Gold products (in USD)') + 
  theme_bw()
```


##### Observations for Mnt's
We noticed that there is a pattern worth studying forward: 

*Overall, the more the clients spend in any category of products, the more likely they are to respond better to our ad.

In the next section (Statistical analysis), we will determine whether these differences are **statistical significant** or not to decided if we can use it in our model to **predict the outcome**.



## Section 4: Statistical Analysis
***

Before we start the statistical tests, we created a table defining which variables we are going to perform the tests on.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
statistical_analysis_features <- data.frame(
  Group = c("ID", "Age", "Income", "Kidhome", "Teenhome", "Dt_Customer", "Recency", "MntWines","MntFruits","MntMeatProducts","MntFishProducts","MntSweetProducts","MntGoldProds","NumDealsPurchases","NumWebPurchases","NumCatalogPurchases","NumStorePurchases","NumWebVisitsMonth","AcceptedCpm1", "AcceptedCpm2", "AcceptedCpm3", "AcceptedCpm4", "AcceptedCpm5", "Complain", "Z_CostContact", "Z_Revenue", "Education", "Marital Status"),
    
Pursue_a_statistical_analysis= c("NO",
            "NO", "YES", "YES", "YES", "YES", "YES", "YES", "YES", "YES", "YES,", "YES", "YES", "NO", "YES", "YES", "NO", "YES", "YES", "YES", "YES", "YES", "YES", "YES", "NO", "NO", "YES", "YES")

)
```

```{r , echo=FALSE, message=FALSE, warning=FALSE}
kable(statistical_analysis_features, caption = "Which features are we going to keep analyzing?")
```

### Filter by Response
Also, it would be useful to filter the Data by response for the tests.
```{r}
Data_0 <- Data %>%
  filter(Response == 0)
nrow(Data_0)

Data_1 <- Data %>%
  filter(Response == 1)
nrow(Data_1)
```
The Data_1 dataframe has 323 observations, and the data_0 dataframe has 1830.

### Permutation Tests for numerical continuous features
In this test we are going to compare the difference of the median for the Response (0 vs 1) to determine whether our findings are statistical significant or random chance.

To avoid making the analysis longer, we are just going to show the calculations for the first feature (Income), then we are just going to show the result of the analysis for the remaining features.

***
#### Income

```{r}
median_Income_0 <- median(Data_0$Income)
median_Income_0

median_Income_1 <- median(Data_1$Income)
median_Income_1
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(boot)
stat_fun_Income_1 <- function(x, idx) median(x[idx])
boot_obj_Income_1 <- boot(Data_1$Income, R=1000, statistic=stat_fun_Income_1)
boot_obj_Income_1
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(boot)
stat_fun_Income_0 <- function(x, idx) median(x[idx])
boot_obj_Income_0 <- boot(Data_0$Income, R=1000, statistic=stat_fun_Income_0)
boot_obj_Income_0
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
boot_ci_Income_1 <- boot.ci(boot_obj_Income_1, conf=0.95, type='basic')
X_Income_1 <- data.frame(median=boot_obj_Income_1$t)
ci90_Income_1 <- boot_ci_Income_1$basic[4:5]
ci_Income_1 <- data.frame(ci_Income_1=ci90_Income_1, y=c(8, 12))
ci_Income_1
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
boot_ci_Income_0 <- boot.ci(boot_obj_Income_0, conf=0.95, type='basic')
X_Income_0 <- data.frame(median=boot_obj_Income_0$t)
ci90_Income_0 <- boot_ci_Income_0$basic[4:5]
ci_Income_0 <- data.frame(ci_Income_0=ci90_Income_0, y=c(8, 12))
ci_Income_0
```

##### Density plot of the bootstrap (95% confidence) - median income for both responses
```{r, echo=FALSE, message=FALSE, warning=FALSE }
ggplot() +
  stat_density(data = X_Income_1, aes(x = median, group = 1, fill = "Response 1"), alpha = 0.5) +
  stat_density(data = X_Income_0, aes(x = median, group = 1, fill = "Response 0"), alpha = 0.5) +
  geom_vline(data = X_Income_0, aes(xintercept = median_Income_0), linetype = 2, color = "#F8766D") +
  geom_vline(data = X_Income_1, aes(xintercept = median_Income_1), linetype = 2, color = "#00BFC4") +
  theme_bw() +
  labs(title = "Density curve of response 1 vs 0", x = "Median samples", y = "Density", fill = "") +
  scale_fill_manual(values = c("#F8766D", "#00BFC4"), labels = c("Response 0", "Response 1"))
```



```{r, , echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
perm_fun <- function(x, nA, nB)
{
  n <- nA + nB
  idx_b <- sample(1:n, nB)
  idx_a <- setdiff(1:n, idx_b)
  median_diff <- median(x[idx_b]) - median(x[idx_a])
  return(median_diff)
}
```


##### Results of the permutation test for Income
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$Income, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-10000, 25000))
abline(v=median_Income_1 - median_Income_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Income_1 - median_Income_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Income_1 - median_Income_0))
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that Income could be a pontential feature for the model to make predictions.




























***
#### MntWines

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Wines_0 <- median(Data_0$MntWines)
median_Wines_0

median_Wines_1 <- median(Data_1$MntWines)
median_Wines_1
```


##### Results of the permutation test for MntWines
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntWines, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-100, 400))
abline(v=median_Wines_1 - median_Wines_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Wines_1 - median_Wines_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Wines_1 - median_Wines_0))
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntWines could be a potential feature for the model to make predictions.


























***
#### MntFruits

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Fruits_0 <- median(Data_0$MntFruits)
median_Fruits_0

median_Fruits_1 <- median(Data_1$MntFruits)
median_Fruits_1
```


##### Results of the permutation test for MntFruits
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntFruits, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-5, 20))
abline(v=median_Fruits_1 - median_Fruits_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Fruits_1 - median_Fruits_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Fruits_1 - median_Fruits_0))
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntFruits could be a potential feature for the model to make predictions.




































***
#### MntMeatProducts	

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Meat_0 <- median(Data_0$MntMeatProducts)
median_Meat_0

median_Meat_1 <- median(Data_1$MntMeatProducts)
median_Meat_1
```


##### Results of the permutation test for MntMeatProducts
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntMeatProducts, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-50, 170))
abline(v=median_Meat_1 - median_Meat_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Meat_1 - median_Meat_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Meat_1 - median_Meat_0))
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntMeatProducts could be a potential feature for the model to make predictions.


































***
#### MntFishProducts	

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Fish_0 <- median(Data_0$MntFishProducts)
median_Fish_0

median_Fish_1 <- median(Data_1$MntFishProducts)
median_Fish_1
```


##### Results of the permutation test for MntFishProducts
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntFishProducts, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-5, 25))
abline(v=median_Fish_1 - median_Fish_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Fish_1 - median_Fish_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Fish_1 - median_Fish_0))
```




The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntFishProducts could be a potential feature for the model to make predictions.


























***
#### MntSweetProducts	

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Sweet_0 <- median(Data_0$MntSweetProducts	)
median_Sweet_0

median_Sweet_1 <- median(Data_1$MntSweetProducts	)
median_Sweet_1
```


##### Results of the permutation test for MntSweetProducts
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntSweetProducts, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-5, 25))
abline(v=median_Sweet_1 - median_Sweet_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Sweet_1 - median_Sweet_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Sweet_1 - median_Sweet_0))
```


The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntSweetProducts could be a potential feature for the model to make predictions.









***
#### MntGoldProds

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
median_Gold_0 <- median(Data_0$MntGoldProds	)
median_Gold_0

median_Gold_1 <- median(Data_1$MntGoldProds	)
median_Gold_1
```


##### Results of the permutation test for MntGoldProds
```{r, echo=FALSE, message=FALSE, warning=FALSE}
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
  perm_diffs[i] = perm_fun(Data$MntGoldProds, 1830, 323)
}
par(mar=c(4,4,1,0)+.1)
hist(perm_diffs, xlab='Difference of the median for Response 1 and 0', main='', xlim=c(-5, 25))
abline(v=median_Gold_1 - median_Gold_0, lty=2, lwd=1.5)
text('  Observed\n  difference', x=median_Gold_1 - median_Gold_0,  y=par()$usr[4]-20, adj=0)

median(perm_diffs > (median_Gold_1 - median_Gold_0))
```


The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that MntGoldProds could be a potential feature for the model to make predictions.






### Permutation Tests for categorical nominal features with 2 possible values
In this test we are going to compare the counts for the Response (0 vs 1) to determine whether our findings are statistical significant or random chance.

To avoid making the analysis longer, we are just going to show the calculations for the first feature (AcceptedCmp1), then we are just going to show the result of the analysis for the remaining features.

***
#### AcceptedCmp1

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Cmp1 <- Data %>%
  group_by(AcceptedCmp1, Response) %>%
  count(AcceptedCmp1, sort = TRUE) %>%
  return(AcceptedCmp1)

Count_Cmp1
```

Then we calculate the % of conversion for people who AcceptedCmp1 vs people who didn't AccepetedCmp1, and we substract them. 
```{r}
obs_pct_diff_Cmp1 <- 100 * (79/141 -244/2012) #%conv1 - %conv2
obs_pct_diff_Cmp1
```


```{r,echo=FALSE, message=FALSE, warning=FALSE}
perm_fun_contar <- function(x, nA, nB)
{
  n <- nA + nB
  idx_b <- sample(1:n, nB)
  idx_a <- setdiff(1:n, idx_b)
  
  ones_b <- sum(x[idx_b] == 1)
  zeros_b <- sum(x[idx_b] == 0)
  
  ones_a <- sum(x[idx_a] == 1)
  zeros_a <- sum(x[idx_a] == 0)
  
  pct_ones_b <- ones_b / length(idx_b)
  pct_ones_a <- ones_a / length(idx_a)
  
  diff_pct_ones <- pct_ones_a - pct_ones_b
  
  return(diff_pct_ones)
}
```

##### Results of the permutation test for AcceptedCmp1
Now we are going to determine whether this difference is statistical significant.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(1)
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 141, 2012) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-10, 55))
abline(v=obs_pct_diff_Cmp1, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Cmp1,  y=par()$usr[4]-20, adj=0)

# Obbserved difference
obs_pct_diff_Cmp1

### P-Value

mean(perm_diffs > obs_pct_diff_Cmp1)
```



The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that AcceptedCmp1 could be a potential feature for the model to make predictions.









***
#### AcceptedCmp2

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Cmp2 <- Data %>%
  group_by(AcceptedCmp2, Response) %>%
  count(AcceptedCmp2, sort = TRUE) %>%
  return(AcceptedCmp2)

Count_Cmp2
```

Then we calculate the % of conversion for people who AcceptedCmp1 vs people who didn't AccepetedCmp1, and we substract them. 
```{r}
obs_pct_diff_Cmp2 <- 100 * (20/30 -303/2123) #%conv1 - %conv2 of response by accepted cmp
obs_pct_diff_Cmp2
```


##### Results of the permutation test for AcceptedCmp2
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(1)
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 30, 2123) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-25, 65))
abline(v=obs_pct_diff_Cmp2, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Cmp2,  y=par()$usr[4]-20, adj=0)

# Obbserved difference
obs_pct_diff_Cmp2

### P-Value

mean(perm_diffs > obs_pct_diff_Cmp2)
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that AcceptedCmp2 could be a potential feature for the model to make predictions.



















***
#### AcceptedCmp3

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Cmp3 <- Data %>%
  group_by(AcceptedCmp3, Response) %>%
  count(AcceptedCmp3, sort = TRUE) %>%
  return(AcceptedCmp3)

Count_Cmp3
```

Then we calculate the % of conversion for people who AcceptedCmp1 vs people who didn't AccepetedCmp1, and we substract them. 
```{r}
obs_pct_diff_Cmp3 <- 100 * (77/162 -246/1991) #%conv1 - %conv2 of response by accepted cmp
obs_pct_diff_Cmp3
```


##### Results of the permutation test for AcceptedCmp3
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(1)
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 162, 1991) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-10, 50))
abline(v=obs_pct_diff_Cmp3, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Cmp3,  y=par()$usr[4]-20, adj=0)

# Obbserved difference
obs_pct_diff_Cmp3

### P-Value

mean(perm_diffs > obs_pct_diff_Cmp3)
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that AcceptedCmp3 could be a potential feature for the model to make predictions.






























***
#### AcceptedCmp4

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Cmp4 <- Data %>%
  group_by(AcceptedCmp4, Response) %>%
  count(AcceptedCmp4, sort = TRUE) %>%
  return(AcceptedCmp4)

Count_Cmp4
```

Then we calculate the % of conversion for people who AcceptedCmp1 vs people who didn't AccepetedCmp1, and we substract them. 
```{r}
obs_pct_diff_Cmp4 <- 100 * (59/159 -264/1994) #%conv1 - %conv2 of response by accepted cmp
obs_pct_diff_Cmp4
```


##### Results of the permutation test for AcceptedCmp4
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(1)
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 159, 1994) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-10, 35))
abline(v=obs_pct_diff_Cmp4, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Cmp4,  y=par()$usr[4]-20, adj=0)

# Obbserved difference
obs_pct_diff_Cmp4

### P-Value

mean(perm_diffs > obs_pct_diff_Cmp4)
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that AcceptedCmp4 could be a potential feature for the model to make predictions.
















































***
#### AcceptedCmp5

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Cmp5 <- Data %>%
  group_by(AcceptedCmp5, Response) %>%
  count(AcceptedCmp5, sort = TRUE) %>%
  return(AcceptedCmp5)

Count_Cmp5
```

Then we calculate the % of conversion for people who AcceptedCmp1 vs people who didn't AccepetedCmp1, and we substract them. 
```{r}
obs_pct_diff_Cmp5 <- 100 * (91/161 -232/1992) #%conv1 - %conv2 of response by accepted cmp
obs_pct_diff_Cmp5
```


##### Results of the permutation test for AcceptedCmp5
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(1)
perm_diffs <- rep(0, 1000)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 161, 1992) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-10, 55))
abline(v=obs_pct_diff_Cmp5, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Cmp5,  y=par()$usr[4]-20, adj=0)

# Obbserved difference
obs_pct_diff_Cmp5

### P-Value

mean(perm_diffs > obs_pct_diff_Cmp5)
```

The result is a p-value of 0, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that AcceptedCmp5 could be a potential feature for the model to make predictions.




























***
#### Complain

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Complain <- Data %>%
  group_by(Complain, Response) %>%
  count(Complain, sort = TRUE) %>%
  return(Complain)

Count_Complain
```

Then we calculate the % of conversion for people who Complain vs people who didn't Complain, and we substract them. 
```{r}
obs_pct_diff_Complain <- 100 * (320/2133-3/20) #%conv1 - %conv2 of response by accepted cmp
obs_pct_diff_Complain
#result is 0.002344116
```


##### Results of the permutation test for Complain
```{r,echo=FALSE, message=FALSE, warning=FALSE}
## Statistical Significance and P-Values
conversion <- c(rep(0, 1830), rep(1, 323)) # definir cuantos 0 y 1 hay en response
set.seed(123)
perm_diffs <- rep(0, 1300)
for (i in 1:1000) {
perm_diffs[i] = 100 * perm_fun_contar(conversion, 2133, 20) #denominador de conv1-conv2
}

hist(perm_diffs, xlab='Difference between conversion rates (percent)', main='', xlim=c(-25, 35))
abline(v=obs_pct_diff_Complain, lty=2, lwd=1.5)
text('   Observed\n   difference', x=obs_pct_diff_Complain,  y=par()$usr[4]-30, adj=0)

# Obbserved difference
obs_pct_diff_Complain

### P-Value

mean(perm_diffs > obs_pct_diff_Complain)
```
##### Observations for Complain
The result is a p-value of 41.1%, this means that in 41.1% of the time it can be a result of random chance. Therefore, the null hypothesis is proven and we conclude that **this result is not statistical significant**.

Therefore, we will **not consider this features for the model to make predictions**.

### Chi-square Tests for categorical nominal features with more than 2 possible values

In this test we are going to compare the counts for the Response (0 vs 1) to determine whether our findings are statistical significant or random chance.

To avoid making the analysis longer, we are just going to show the calculations for the first feature (kidhome), then we are just going to show the result of the analysis for the remaining features.

***
#### Kidhome

We start by making a table with the counts.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
Count_Kidhome <- Data %>%
  group_by(Kidhome, Response) %>%
  count(Kidhome, sort = TRUE) %>%
  arrange(Kidhome) %>%
  return(Kidhome)

Count_Kidhome
```
```{r}
reaction_Kidhome <- matrix(Count_Kidhome$n, nrow=3, ncol=2, byrow=TRUE)
reaction_Kidhome
dimnames(reaction_Kidhome) <- list(unique(Data$Kidhome), unique(Data$Response))
reaction_Kidhome
```
```{r}
chisq.test(reaction_Kidhome, simulate.p.value=TRUE)
```
The result is a p-value of 0.0009995, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that Kidhome could be a potential feature for the model to make predictions.












***
#### Teenhome

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
Count_Teenhome <- Data %>%
  group_by(Teenhome, Response) %>%
  count(Teenhome, sort = TRUE) %>%
  arrange(Teenhome) %>%
  return(Teenhome)

Count_Teenhome
```

```{r ,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
reaction_Teenhome <- matrix(Count_Teenhome$n, nrow=3, ncol=2, byrow=TRUE)
reaction_Teenhome
dimnames(reaction_Teenhome) <- list(unique(Data$Teenhome), unique(Data$Response))
reaction_Teenhome
```



```{r}
chisq.test(reaction_Teenhome, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that Teenhome could be a potential feature for the model to make predictions.








***
#### Dt_Customer

For this particular feature, in order to perform the Chi-square test, I had to divide the Dt_Customer in periods of 6 months.
```{r}
# Create a new column with the 6-month period
Data$Period <- cut(Data$Dt_Customer, breaks = "6 months")

# Count the number of dates in each period
table(Data$Period)
```



```{r}
Count_Period <- Data %>%
  group_by(Period, Response) %>%
  count(Period, sort = TRUE) %>%
  arrange(Period) %>%
  return(Period)

Count_Period
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Extract unique values of Period column and convert to list
Lista_periodos <- Count_Period %>% 
                 pull(Period) %>% 
                 unique() 
```


```{r}
reaction_Period <- matrix(Count_Period$n, nrow=4, ncol=2, byrow=TRUE)
reaction_Period
dimnames(reaction_Period) <- list(Lista_periodos, unique(Data$Response))
reaction_Period
```

```{r}
chisq.test(reaction_Period, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that Dt_Customer could be a potential feature for the model to make predictions.






***
#### Recency

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Create a new column with the group of 10s
Data$Group_Recency <- cut(Data$Recency, breaks = seq(0, 100, by = 10), right = FALSE)

# Count the number of values in each group
table(Data$Group_Recency)
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
Count_Recency <- Data %>%
  group_by(Group_Recency, Response) %>%
  count(Group_Recency, sort = TRUE) %>%
  arrange(Group_Recency) %>%
  return(Group_Recency)

Count_Recency
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Extract unique values of Period column and convert to list
Lista_Recency <- Count_Recency %>% 
                 pull(Group_Recency) %>% 
                 unique() 
Lista_Recency
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
reaction_Recency <- matrix(Count_Recency$n, nrow=10, ncol=2, byrow=TRUE)
reaction_Recency
dimnames(reaction_Recency) <- list(Lista_Recency, unique(Data$Response))
reaction_Recency
```


```{r}
chisq.test(reaction_Recency, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that Recency could be a potential feature for the model to make predictions.













***
#### NumWebPurchases

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Create a new column with the group of 10s
Data$Group_NumWebPurchases <- cut(Data$NumWebPurchases, breaks = seq(0, 12, by = 6), right = FALSE)

# Count the number of values in each group
table(Data$Group_NumWebPurchases)
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
Count_NumWebPurchases <- Data %>%
  group_by(Group_NumWebPurchases, Response) %>%
  count(Group_NumWebPurchases, sort = TRUE) %>%
  arrange(Group_NumWebPurchases) %>%
  return(Group_NumWebPurchases)

Count_NumWebPurchases
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Extract unique values of Period column and convert to list
Lista_NumWebPurchases <- Count_NumWebPurchases %>% 
                 pull(Group_NumWebPurchases) %>% 
                 unique() 
Lista_NumWebPurchases
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
reaction_NumWebPurchases <- matrix(Count_NumWebPurchases$n, nrow=2, ncol=2, byrow=TRUE)
reaction_NumWebPurchases
dimnames(reaction_NumWebPurchases) <- list(Lista_NumWebPurchases, unique(Data$Response))
reaction_NumWebPurchases
```


```{r}
chisq.test(reaction_NumWebPurchases, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that NumWebPurchases could be a potential feature for the model to make predictions.











***
#### NumCatalogPurchases

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Create a new column with the group of 10s
Data$Group_NumCatalogPurchases <- cut(Data$NumCatalogPurchases, breaks = seq(0, 12, by = 4), right = FALSE)

# Count the number of values in each group
table(Data$Group_NumCatalogPurchases)
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
Count_NumCatalogPurchases <- Data %>%
  group_by(Group_NumCatalogPurchases, Response) %>%
  count(Group_NumCatalogPurchases, sort = TRUE) %>%
  arrange(Group_NumCatalogPurchases) %>%
  return(Group_NumCatalogPurchases)

Count_NumCatalogPurchases
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Extract unique values of Period column and convert to list
Lista_NumCatalogPurchases <- Count_NumCatalogPurchases %>% 
                 pull(Group_NumCatalogPurchases) %>% 
                 unique() 
Lista_NumCatalogPurchases
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
reaction_NumCatalogPurchases <- matrix(Count_NumCatalogPurchases$n, nrow=3, ncol=2, byrow=TRUE)
reaction_NumCatalogPurchases
dimnames(reaction_NumCatalogPurchases) <- list(Lista_NumCatalogPurchases, unique(Data$Response))
reaction_NumCatalogPurchases
```


```{r}
chisq.test(reaction_NumCatalogPurchases, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that NumCatalogPurchases could be a potential feature for the model to make predictions.

































***
#### NumWebVisitsMonth

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Create a new column with the group of 10s
Data$Group_NumWebVisitsMonth <- cut(Data$NumWebVisitsMonth, breaks = seq(0, 12, by = 3), right = FALSE)

# Count the number of values in each group
table(Data$Group_NumWebVisitsMonth)
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
Count_NumWebVisitsMonth <- Data %>%
  group_by(Group_NumWebVisitsMonth, Response) %>%
  count(Group_NumWebVisitsMonth, sort = TRUE) %>%
  arrange(Group_NumWebVisitsMonth) %>%
  return(Group_NumWebVisitsMonth)

Count_NumWebVisitsMonth
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# Extract unique values of Period column and convert to list
Lista_NumWebVisitsMonth <- Count_NumWebVisitsMonth %>% 
                 pull(Group_NumWebVisitsMonth) %>% 
                 unique() 
Lista_NumWebVisitsMonth
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
reaction_NumWebVisitsMonth <- matrix(Count_NumWebVisitsMonth$n, nrow=4, ncol=2, byrow=TRUE)
reaction_NumWebVisitsMonth
dimnames(reaction_NumWebVisitsMonth) <- list(Lista_NumWebVisitsMonth, unique(Data$Response))
reaction_NumWebVisitsMonth
```


```{r}
chisq.test(reaction_NumWebVisitsMonth, simulate.p.value=TRUE)
```
The result is a p-value of 0.0004998, this indicate a strong evidence against the null hypothesis, and therefore we conclude that **this result is statistical significant**.

This indicates that NumWebVisitsMonth could be a potential feature for the model to make predictions.

















### Anova Tests




